{\bf {\Large Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico}}

### 2016-11-28 ident_manu.Rnw
changed author contact, added lowe edits

\begin{singlespace}
\title{{\bf {\Large Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$, Lisa L. Lowe$^2$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
	\\\\{\textit {\normalsize $^2$Lockheed Martin IS \& GS - Civil, supporting the USEPA}}
	\\{\textit {\normalsize Resarch Triangle Park, NC 27709}}
	\\{\textit {\normalsize Phone: 919-541-3985,}}
	\\{\textit {\normalsize Email: \href{mailto:lowe.lisa@epa.gov}{lowe.lisa@epa.gov}}}
  \vspace{1in} 
  \\ \Sexpr{raw}
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

\begin{abstract}
\noindent Bio-geo-chemical models are useful tools in environmental sciences that can guide management and policy-making. Consequently, significant time and resources are spent developing these models in system-specific contexts. The optimization of model parameters to maximize precision, including transferability of these models to different systems, are fundamental concerns in the development and application of these tools. This study describes quantitative limitations of coupled hydrodynamic-ecological modelling by contrasting numeric and ecological certainty with a systematic framework for characterizing parameter sensitivity and identifability.  We evaluate a simple bio-geo-chemical model that is the \ac{zerod} unit of a larger spatio-temporal model of hypoxia on the \acl{lcs} of Gulf of Mexico as an example. Results from analysis of the \ac{zerod} model are used to infer larger trends in dissolved oxygen dynamics over time, having implications for understanding factors that contribute to environmental conditions that are detrimental to aquatic resources.  In particular, we focus on issues of parameter identifiability using local sensitivity analyses to provide quantitative descriptions of numerical constraints on model precision.  We argue that quantitative and ecological certainty in model calibration are often at odds and practitioners must choose explicit model components to optimize given tradeoffs between the two. We further conclude that numerically optimal parameter sets for models of hypoxia are often small subsets of the complete parameter set because of redundancies in the unique effects of paramater perturbations on model output.  As a result, we demonstrate that use of a model for inference into ecological mechanisms of observed or predicted changes in hypoxic condition can be potentially misguided in the absence of quantitative descriptions of identifiability.  Although these concerns have been expressed in the literature, they are rarely explicitly addressed or included in model evaluations.  In addition to immediate implications for regional models, we provide a framework for describing the effects of parameter uncertainty and identifiability that can be applied to similar models to better inform environmental management.
\end{abstract}
\acresetall

@@

This study evaluated a recently developed hydrodynamic and ecological model that describes horizontal and vertical transport and mixing of state variables relevant for hypoxia in the northern \ac{gom}.  The \ac{cgem} includes elements from the Navy Coastal Ocean Model \citep{Martin00} that describes hydrodynamics on the \ac{lcs} and a biogeochemical model with multiple plankton groups, water-column metabolism, and sediment diagenesis \citep{Eldridge10}.  The hydrodynamic component of \ac{cgem} provides a spatially-explicit description of hypoxia using an orthogonal grid with an approximate horizontal resolution of 1.9 km$^2$ and twenty equally-spaced vertical sigma layers on the shelf (depth $\leq$ 100 m, with additional hybrid layers at deeper depths).  The biogeochemical component includes equations for 36 state variables including six phytoplankton groups (with nitrogen and phosophorus quotas for each), two zooplankton groups, nitrate, ammonium, phosphate, dissolved inorganic carbon, oxygen, silica, and multiple variables for dissolved and particulate organic matter from different sources.  Atmospheric and hydrological boundary conditions described in \citet{Hodur97} and \citet{Lehrter13} are also included in \ac{cgem}.

The core unit of \ac{cgem} is FishTank, a \ac{zerod} model that implements the biogeochemical equations in \citet{Eldridge10} and does not include any form of physical transport (i.e., advection, mixing, or surface flux).  Although FishTank was developed for specific application in \ac{cgem}, it can easily be applied to other hydrodynamic grids. Accordingly, the sensitivity and identifiability analyses described below are informative for both the \ac{lcs} gridded model as well as potential applications to different systems.  The FishTank model provides estimates for the 36 state variables described above using a \ac{zerod} parcel that is uniformly mixed as a closed system.  A set of initial conditions is provided on execution of the model that is based on observations of relevant variables obtained from research cruises in the northern \ac{gom} during April, June, and September of 2006 \citep[Table 1 in][]{Murrell14}.

Results from FishTank are based on time-dependent differential equations that describe energy flow between phytoplankton and zooplankton groups as affected by nutrient uptake rates, organic matter inputs and losses, inherent optical properties, sediment diagenesis, and temperature (\citealt{Penta08,Eldridge10}, see appendix in \citetalias{LehrterIR}).  A total of 108 equations are estimated at each time step to return a value for each of the 36 state variables described by the model.  In addition to the initial conditions, 251 parameter values for each of the equations are also supplied at model execution.  These parameters define relationships among fixed effects in the equations and represent ecological properties described by the model that influence hypoxia formation.  Values for each of the parameters were based on estimates from the literature, field or laboratory-based measurements, or expert knowledge in absence of the former.  As such, a sensitivity analysis of parameter values is warranted given that, for example, literature or field-based estimates may not apply under all scenarios or expert knowledge is not completely certain \citep{Refsgaard07}.

@@

The above analyses were repeated for additional state variables estimated by FishTank to provide further descriptions of ecological dynamics that are relevant for hypoxia.  In addition to \ac{do}, other state variables that were evaluated were \ac{chla}, irradiance, nitrate, ammonium, particulate organic matter, dissolved organic matter, and phosphorus.  Particulate and dissolved organic matter were estimated as the summation of the respective outputs for organic matter from phytoplankon (\textit{OM1\_A}, \textit{OM2\_A}), fecal pellets (\textit{OM1\_fp}, \textit{OM2\_fp}), river sources \textit{OM1\_rp}, \textit{OM2\_rp}), and boundary conditions (\textit{OM1\_bc}, \textit{OM2\_bc}, see \citetalias{LehrterIR}).

@@

% do sensitivity all categories
<<dosens, eval = T, cache = F>>=
senstab(out_var = 'O2', tablab = 'dosens', captxt = '\\ac{do}', digits = 2, pow = 2, tabsize = 'footnotesize')
@

@@

% parameter exclusion temp
<<exclex, eval = T, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) of organic matter parameters for subset combinations in \\cref{fig:identbox}.  Identifiability is evaluated for subsets that excluded and included the parameters at the top of each plot. Identifiability of including all eight parameters is in \\cref{fig:identbox}. Grey lines indicate potential thresholds at $\\gamma = 10, 15$ for maximum acceptable identifiability.', fig.height = 7.25, fig.width = 7.25, echo = F, cache = TRUE, out.width = "\\textwidth">>=
data(cat_ident_all)

>>>>

\begin{singlespace}
\title{{\bf {\Large Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^2$, Lisa L. Lowe$^3$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Email: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}}}
	  \\\\{\textit {\normalsize $^2$Dauphin Island Sea Lab, University of South Alabama}}
  \\{\textit {\normalsize Dauphin Island, AL 36528}}
	\\{\textit {\normalsize Phone: 251-861-2141 ext. 7567}}
	\\{\textit {\normalsize Email: \href{mailto:jlehrter@disl.org}{jlehrter@disl.org}}}
	\\\\{\textit {\normalsize $^3$Lockheed Martin IS \& GS - Civil, supporting the USEPA}}
	\\{\textit {\normalsize Resarch Triangle Park, NC 27709}}
	\\{\textit {\normalsize Phone: 919-541-3985,}}
	\\{\textit {\normalsize Email: \href{mailto:lowe.lisa@epa.gov}{lowe.lisa@epa.gov}}}
  \vspace{1in} 
  \\ \Sexpr{raw}
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

\begin{abstract}
\noindent Bio-geo-chemical models are useful tools in environmental sciences that can guide management and policy-making. Consequently, significant time and resources are spent developing these models in system-specific contexts. The optimization of model parameters to maximize precision, including transferability of these models to different systems, are fundamental concerns in the development and application of these tools. This study provides a context for understanding quantitative limitations of coupled hydrodynamic-ecological models by evaluating parameter sensitivity and identifability of a \ac{zerod} unit of a larger spatio-temporal model of hypoxia on the \acl{lcs} of Gulf of Mexico.  The analysis provides a contrast of numeric and ecological certainty in parameter subsets using a systematic framework to infer larger trends in dissolved oxygen dynamics over time, having implications for understanding factors that contribute to environmental conditions that are detrimental to aquatic resources.  In particular, we focus on issues of parameter identifiability using local sensitivity analyses to provide quantitative descriptions of numerical constraints on model precision.  We argue that quantitative and ecological certainty in model calibration are often at odds and practitioners must choose explicit model components to optimize given tradeoffs between the two. We further conclude that numerically optimal parameter sets for models of hypoxia are often small subsets of the complete parameter set because of redundancies in the unique effects of paramater perturbations on model output.  As a result, we demonstrate that use of a model for inference into ecological mechanisms of observed or predicted changes in hypoxic condition can be potentially misguided in the absence of quantitative descriptions of identifiability.  Although these concerns have been expressed in the literature, they are rarely explicitly addressed or included in model evaluations.  In addition to immediate implications for regional models, we provide a framework for describing the effects of parameter uncertainty and identifiability that can be applied to similar models to better inform environmental management.
\end{abstract}
\acresetall

@@

This study evaluated the core unit of a recently developed hydrodynamic and ecological model that describes horizontal and vertical transport and mixing of state variables relevant for hypoxia in the northern \ac{gom}.  The \ac{cgem} includes elements from the Navy Coastal Ocean Model \citep{Martin00} that describes hydrodynamics on the \ac{lcs} and a biogeochemical model with multiple plankton groups, water-column metabolism, and sediment diagenesis \citep{Eldridge10}.  The hydrodynamic component of \ac{cgem} provides a spatially-explicit description of hypoxia using an orthogonal grid with an approximate horizontal resolution of 1.9 km$^2$ and twenty equally-spaced vertical sigma layers on the shelf (depth $\leq$ 100 m, with additional hybrid layers at deeper depths).  The biogeochemical component includes equations for 36 state variables including six phytoplankton groups (with nitrogen and phosophorus quotas for each), two zooplankton groups, nitrate, ammonium, phosphate, dissolved inorganic carbon, oxygen, silica, and multiple variables for dissolved and particulate organic matter from different sources.  Atmospheric and hydrological boundary conditions described in \citet{Hodur97} and \citet{Lehrter13} are also included in \ac{cgem}.

The core unit of \ac{cgem} is FishTank, a \ac{zerod} model that implements the biogeochemical equations in \citet{Eldridge10} and does not include any form of physical transport (i.e., advection, mixing, or surface flux) nor sediment diagenesis.  Although FishTank was developed for specific application in \ac{cgem}, it can easily be applied to other hydrodynamic grids. Accordingly, the sensitivity and identifiability analyses described below focused exclusively on FishTank and are informative for both the \ac{lcs} gridded model as well as potential applications to different systems.  The FishTank model provides estimates for the 36 state variables described above using a \ac{zerod} parcel that is uniformly mixed as a closed system.  A set of initial conditions is provided on execution of the model that is based on observations of relevant variables obtained from research cruises in the northern \ac{gom} during April, June, and September of 2006 \citep[Table 1 in][]{Murrell14}.

Results from FishTank are based on time-dependent differential equations that describe energy flow between phytoplankton and zooplankton groups as affected by nutrient uptake rates, organic matter inputs and losses, inherent optical properties, and temperature (\citealt{Penta08,Eldridge10}, see appendix in \citetalias{LehrterIR}).  A total of 108 equations are estimated at each time step to return a value for each of the 36 state variables described by the model.  In addition to the initial conditions, 251 parameter values for each of the equations are also supplied at model execution.  These parameters define relationships among fixed effects in the equations and represent ecological properties described by the model that influence hypoxia formation.  Values for each of the parameters were based on estimates from the literature, field or laboratory-based measurements, or expert knowledge in absence of the former.  As such, a sensitivity analysis of parameter values is warranted given that, for example, literature or field-based estimates may not apply under all scenarios or expert knowledge is not completely certain \citep{Refsgaard07}.

@@

The above analyses were repeated for additional state variables estimated by FishTank to provide further descriptions of ecological dynamics that are relevant for hypoxia.  In addition to \ac{do}, other state variables that were evaluated were \ac{chla}, irradiance, nitrate, ammonium, particulate organic matter, dissolved organic matter, and phosphorus.  Particulate and dissolved organic matter were estimated as the summation of the respective outputs for organic matter from phytoplankon (\textit{OM1\_A}, \textit{OM2\_A}) and fecal pellets from zooplankton (\textit{OM1\_Z}, \textit{OM2\_Z}, see \citetalias{LehrterIR}).

@@

% do sensitivity all categories
<<dosens, eval = T, cache = F>>=
senstab(out_var = 'O2', tablab = 'dosens', captxt = '\\ac{do}', digits = 2, pow = 2, tabsize = 'footnotesize', foot.val = '\\footnotesize *Temperature parameters apply separately to phytoplankton ($p1$, one group) or zooplankton ($z1$, one group), denoted by subscripts')
@

@@

% parameter exclusion temp
<<exclex, eval = T, fig.cap = 'Identifiability (as $\\gamma$, \\cref{gameq}) for \\ac{do} of organic matter parameters for subset combinations in \\cref{fig:identplo}.  Identifiability is evaluated for subsets that excluded and included the parameters at the top of each plot. Identifiability of including all eight parameters is in \\cref{fig:identplo}. Grey lines indicate potential thresholds at $\\gamma = 10, 15$ for maximum acceptable identifiability.', fig.height = 7.25, fig.width = 7.25, echo = F, cache = TRUE, out.width = "\\textwidth">>=
data(cat_ident_all)

### 2016-11-28 ident_manu.tex
changed author contact, added lowe edits

\begin{singlespace}
\title{{\bf {\Large Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^1$, Lisa L. Lowe$^2$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Emails: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}, \href{mailto:lehrter.john@epa.gov}{lehrter.john@epa.gov}}}
	\\\\{\textit {\normalsize $^2$Lockheed Martin IS \& GS - Civil, supporting the USEPA}}
	\\{\textit {\normalsize Resarch Triangle Park, NC 27709}}
	\\{\textit {\normalsize Phone: 919-541-3985,}}
	\\{\textit {\normalsize Email: \href{mailto:lowe.lisa@epa.gov}{lowe.lisa@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Wed Sep 28 15:23:05 2016 -0500
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

\begin{abstract}
\noindent Bio-geo-chemical models are useful tools in environmental sciences that can guide management and policy-making. Consequently, significant time and resources are spent developing these models in system-specific contexts. The optimization of model parameters to maximize precision, including transferability of these models to different systems, are fundamental concerns in the development and application of these tools. This study describes quantitative limitations of coupled hydrodynamic-ecological modelling by contrasting numeric and ecological certainty with a systematic framework for characterizing parameter sensitivity and identifability.  We evaluate a simple bio-geo-chemical model that is the \ac{zerod} unit of a larger spatio-temporal model of hypoxia on the \acl{lcs} of Gulf of Mexico as an example. Results from analysis of the \ac{zerod} model are used to infer larger trends in dissolved oxygen dynamics over time, having implications for understanding factors that contribute to environmental conditions that are detrimental to aquatic resources.  In particular, we focus on issues of parameter identifiability using local sensitivity analyses to provide quantitative descriptions of numerical constraints on model precision.  We argue that quantitative and ecological certainty in model calibration are often at odds and practitioners must choose explicit model components to optimize given tradeoffs between the two. We further conclude that numerically optimal parameter sets for models of hypoxia are often small subsets of the complete parameter set because of redundancies in the unique effects of paramater perturbations on model output.  As a result, we demonstrate that use of a model for inference into ecological mechanisms of observed or predicted changes in hypoxic condition can be potentially misguided in the absence of quantitative descriptions of identifiability.  Although these concerns have been expressed in the literature, they are rarely explicitly addressed or included in model evaluations.  In addition to immediate implications for regional models, we provide a framework for describing the effects of parameter uncertainty and identifiability that can be applied to similar models to better inform environmental management.
\end{abstract}
\acresetall

@@

%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), size = tabsize, label = paste0("tab:",         tablab))%

@@

~~turnover rate for OM1A and OM1G&\textit{KG1}&$6.15\times 10^{-3}$\tabularnewline
~~turnover rate for OM2A and OM2G&\textit{KG2}&$3.14\times 10^{-3}$\tabularnewline

@@

@@

\caption{Identifiability (as $\gamma$, \cref{gameq}) of organic matter parameters for subset combinations in \cref{fig:identbox}.  Identifiability is evaluated for subsets that excluded and included the parameters at the top of each plot. Identifiability of including all eight parameters is in \cref{fig:identbox}. Grey lines indicate potential thresholds at $\gamma = 10, 15$ for maximum acceptable identifiability.}\label{fig:exclex}
\end{figure}

@@

~~turnover rate for OM1A and OM1G&\textit{KG1}&$0.07$\tabularnewline

@@

~~turnover rate for OM2A and OM2G&\textit{KG2}&$0.03$\tabularnewline

@@

~~turnover rate for OM1A and OM1G&\textit{KG1}&$0.03$\tabularnewline
~~turnover rate for OM2A and OM2G&\textit{KG2}&$0.01$\tabularnewline

@@

~~turnover rate for OM1A and OM1G&\textit{KG1}&$3.96\times 10^{-3}$\tabularnewline
~~turnover rate for OM2A and OM2G&\textit{KG2}&$9.88\times 10^{-4}$\tabularnewline

@@

~~turnover rate for OM1A and OM1G&\textit{KG1}&$0.02$\tabularnewline
~~turnover rate for OM2A and OM2G&\textit{KG2}&$0.01$\tabularnewline

@@

~~turnover rate for OM1A and OM1G&\textit{KG1}&$0.92$\tabularnewline

@@

~~turnover rate for OM2A and OM2G&\textit{KG2}&$0.01$\tabularnewline

@@

~~turnover rate for OM2A and OM2G&\textit{KG2}&$0.94$\tabularnewline

@@

~~turnover rate for OM1A and OM1G&\textit{KG1}&$0.04$\tabularnewline

@@

~~turnover rate for OM1A and OM1G&\textit{KG1}&$0.14$\tabularnewline
~~turnover rate for OM2A and OM2G&\textit{KG2}&$0.06$\tabularnewline

>>>>

\begin{singlespace}
\title{{\bf {\Large Parameter sensitivity and identifiability for a biogeochemical model of hypoxia in the northern {G}ulf of {M}exico}}}
\author{
  {\bf {\normalsize Marcus W. Beck$^1$, John C. Lehrter$^2$, Lisa L. Lowe$^3$}}
  \\\\{\textit {\normalsize $^1$USEPA National Health and Environmental Effects Research Laboratory}}
  \\{\textit {\normalsize Gulf Ecology Division, 1 Sabine Island Drive, Gulf Breeze, FL 32561}}
	\\{\textit {\normalsize Phone: 850-934-2480, Fax: 850-934-2401}}
	\\{\textit {\normalsize Email: \href{mailto:beck.marcus@epa.gov}{beck.marcus@epa.gov}}}
	  \\\\{\textit {\normalsize $^2$Dauphin Island Sea Lab, University of South Alabama}}
  \\{\textit {\normalsize Dauphin Island, AL 36528}}
	\\{\textit {\normalsize Phone: 251-861-2141 ext. 7567}}
	\\{\textit {\normalsize Email: \href{mailto:jlehrter@disl.org}{jlehrter@disl.org}}}
	\\\\{\textit {\normalsize $^3$Lockheed Martin IS \& GS - Civil, supporting the USEPA}}
	\\{\textit {\normalsize Resarch Triangle Park, NC 27709}}
	\\{\textit {\normalsize Phone: 919-541-3985,}}
	\\{\textit {\normalsize Email: \href{mailto:lowe.lisa@epa.gov}{lowe.lisa@epa.gov}}}
  \vspace{1in} 
  \\ Version Date:   Mon Nov 28 16:09:57 2016 -0600
	}
\date{}
\maketitle
\end{singlespace}
\clearpage

\begin{abstract}
\noindent Bio-geo-chemical models are useful tools in environmental sciences that can guide management and policy-making. Consequently, significant time and resources are spent developing these models in system-specific contexts. The optimization of model parameters to maximize precision, including transferability of these models to different systems, are fundamental concerns in the development and application of these tools. This study provides a context for understanding quantitative limitations of coupled hydrodynamic-ecological models by evaluating parameter sensitivity and identifability of a \ac{zerod} unit of a larger spatio-temporal model of hypoxia on the \acl{lcs} of Gulf of Mexico.  The analysis provides a contrast of numeric and ecological certainty in parameter subsets using a systematic framework to infer larger trends in dissolved oxygen dynamics over time, having implications for understanding factors that contribute to environmental conditions that are detrimental to aquatic resources.  In particular, we focus on issues of parameter identifiability using local sensitivity analyses to provide quantitative descriptions of numerical constraints on model precision.  We argue that quantitative and ecological certainty in model calibration are often at odds and practitioners must choose explicit model components to optimize given tradeoffs between the two. We further conclude that numerically optimal parameter sets for models of hypoxia are often small subsets of the complete parameter set because of redundancies in the unique effects of paramater perturbations on model output.  As a result, we demonstrate that use of a model for inference into ecological mechanisms of observed or predicted changes in hypoxic condition can be potentially misguided in the absence of quantitative descriptions of identifiability.  Although these concerns have been expressed in the literature, they are rarely explicitly addressed or included in model evaluations.  In addition to immediate implications for regional models, we provide a framework for describing the effects of parameter uncertainty and identifiability that can be applied to similar models to better inform environmental management.
\end{abstract}
\acresetall

@@

%latex.default(totab, file = "", rowlabel = "Description", caption = cap.val,     caption.loc = "top", rowname = Description, rgroup = unique(cats),     n.rgroup = as.numeric(table(cats)), size = tabsize, label = paste0("tab:",         tablab), insert.bottom = foot.val)%

@@

~~turnover rate for OM1A and OM1Z&\textit{KG1}&$6.15\times 10^{-3}$\tabularnewline
~~turnover rate for OM2A and OM2Z&\textit{KG2}&$3.14\times 10^{-3}$\tabularnewline

@@

\footnotesize *Temperaure parameters apply to phytoplankton ($p1$, one group) or zooplankton ($z1$, one group), denoted by subscripts\end{table}

@@

\caption{Identifiability (as $\gamma$, \cref{gameq}) for \ac{do} of organic matter parameters for subset combinations in \cref{fig:identplo}.  Identifiability is evaluated for subsets that excluded and included the parameters at the top of each plot. Identifiability of including all eight parameters is in \cref{fig:identplo}. Grey lines indicate potential thresholds at $\gamma = 10, 15$ for maximum acceptable identifiability.}\label{fig:exclex}
\end{figure}

@@

~~turnover rate for OM1A and OM1Z&\textit{KG1}&$0.07$\tabularnewline

@@

~~turnover rate for OM2A and OM2Z&\textit{KG2}&$0.03$\tabularnewline

@@

~~turnover rate for OM1A and OM1Z&\textit{KG1}&$0.03$\tabularnewline
~~turnover rate for OM2A and OM2Z&\textit{KG2}&$0.01$\tabularnewline

@@

~~turnover rate for OM1A and OM1Z&\textit{KG1}&$3.96\times 10^{-3}$\tabularnewline
~~turnover rate for OM2A and OM2Z&\textit{KG2}&$9.88\times 10^{-4}$\tabularnewline

@@

~~turnover rate for OM1A and OM1Z&\textit{KG1}&$0.02$\tabularnewline
~~turnover rate for OM2A and OM2Z&\textit{KG2}&$0.01$\tabularnewline

@@

~~turnover rate for OM1A and OM1Z&\textit{KG1}&$0.92$\tabularnewline

@@

~~turnover rate for OM2A and OM2Z&\textit{KG2}&$0.01$\tabularnewline

@@

~~turnover rate for OM2A and OM2Z&\textit{KG2}&$0.94$\tabularnewline

@@

~~turnover rate for OM1A and OM1Z&\textit{KG1}&$0.04$\tabularnewline

@@

~~turnover rate for OM1A and OM1Z&\textit{KG1}&$0.14$\tabularnewline
~~turnover rate for OM2A and OM2Z&\textit{KG2}&$0.06$\tabularnewline
